\chapter{Requirements traceability}
This section explains which components are needed to meet each requirement as stated in the RASD. 

\begin{enumerate}[label=\textbf{R.\arabic*}]
    \subsubsection*{Users}
    \item \lbl{req: reg} {The system shall allow users to register on the platform with their personal information.} \newline
    \textbf{ciao ciao ciao}
    \item \lbl{req: login} {The system shall allow registered users to log in the platform with valid credentials.}
    \item \lbl{req: listT} {The system shall allow all users to see the list of ongoing tournaments.}
    \item \lbl{req: evalA} {The system shall automatically evaluate submissions.}
    \item \lbl{req: ranks} {The system shall allow users to be able to monitor ranking in real-time during battles and tournaments.}
    \item \lbl{req: profile} {The system shall allow users to see other students' profile.}
    
    \subsubsection*{Educators}
    \item \lbl{req: createT} {The system shall allow the educators to create tournaments.}
    \item \lbl{req: manageT} {The system shall allow the educators to manage their tournaments, in particular invites other collaborators and ends the tournament.}
    \item \lbl{req: createB} {The system shall allow the educators to create code kata battles within a tournament.}
     \item \lbl{req: evalM} {The system shall allow educators to manually evaluate students (if needed) right after a battle closes, during the consolidation stage.}
    \item \lbl{req: createBad} {The system shall allow educators to create badges.}
    \item \lbl{req: defineRV} {The system shall allow educators to define rules and variables.}

    \subsubsection*{Students}
    \item \lbl{req: enrollT} {The system shall allow students to subscribe in tournaments.}
    \item \lbl{req: enrollB} {The system shall allow students to enroll in a battle within a tournament.}
    \item \lbl{req: formTeam} {The system shall allow students to form team for battles, by inviting other students.}        
    \item \lbl{req: notifT} {The system shall notify the students about new tournaments within 10 seconds.}
    \item \lbl{req: notifB} {The system shall notify the students about upcoming battles in tournaments in which they are subscribed within 10 seconds.}
     \item \lbl{req: notifInvite} {The system shall notify the students when they receive an invite to participate in a team within 10 seconds.}
     \item \lbl{req: notifGitHub} {The system shall notify the students when the GitHub repository of a battle is available.}
     \item \lbl{req: notifRankB} {The system shall notify the students when the final battle rank became available within 10 seconds.}
     \item \lbl{req: notifRankT} {The system shall notify the students when the final tournament rank became available within 10 seconds.}
\end{enumerate}
